\documentclass{article}
\usepackage{amsmath, amssymb}
\usepackage{graphicx}
\usepackage{geometry}
\usepackage{natbib}
\geometry{a4paper, margin=1in}

\title{ManifoldGL: Information-Geometric Bundle Adapters for \\ Large Language Models}
\author{Jesús Vilela Jato, A.I. Scientist, H.A.L. 9000}
\date{January 2026}

\begin{document}

\maketitle

\vspace{1cm}
\begin{center}
    \textit{To Edurne, my wife, and my family.}
\end{center}
\vspace{1cm}

\begin{abstract}
We present \textbf{ManifoldGL}, a theoretical framework integrating Riemannian geometry, fiber bundles, and sheaf theory into Large Language Models (LLMs). By treating the latent space as a fiber bundle equipped with a learnable Riemannian metric, we enable rigorous lambda calculus operations on fiber sections. Preliminary experiments confirm the successful learning of non-Euclidean geometry (learned $\sigma \approx 2.2$) and strict adherence to geometric constraints (100\% Manifold Faithfulness Rate), though zero-shot performance on abstract reasoning tasks (ARC-AGI) remains at baseline levels in early trials. This work serves as a proof-of-concept for geometrically rigorous neuro-symbolic architectures.
\end{abstract}

\section{Introduction}
Current LLMs operate primarily in Euclidean vector spaces. We propose that hierarchical and compositional semantics are better represented in curved manifolds with fiber bundle structures. ManifoldGL implements these structures via a custom adapter architecture.

\section{Methodology}
Our approach relies on three pillars:
\begin{itemize}
    \item \textbf{Riemannian Geometry}: We parameterize the metric tensor $g_{ij}$ via Cholesky factors to ensure positive definiteness.
    \item \textbf{Natural Gradient Descent}: We utilize Information Geometry to optimize on the statistical manifold, using the Fisher Indormation Matrix.
    \item \textbf{Sheaf Consistency}: We enforce local consistency across data patches using sheaf-theoretic gluing conditions.
\end{itemize}

\section{Preliminary Results}
We evaluated ManifoldGL on the ARC-AGI benchmark.

\begin{table}[h]
    \centering
    \begin{tabular}{lc}
        \hline
        \textbf{Metric} & \textbf{Value} \\
        \hline
        Manifold Faithfulness Rate (MFR) & 100\% \\
        Learned Curvature Parameter ($\sigma$) & $\approx 2.2$ \\
        ARC-AGI Task Accuracy & 0.0\% \\
        \hline
    \end{tabular}
    \caption{Preliminary Experimental Results}
    \label{tab:results}
\end{table}

While the model has not yet solved ARC-AGI tasks, the high MFR indicates that the geometric constraints are being learned and respected. The convergence of $\sigma$ to a non-zero value suggests that the data naturally prefers a non-Euclidean representation.

\section{Conclusion}
ManifoldGL establishes a verified mathematical foundation for geometric deep learning in LLMs. Future work will focus on scaling training to unlock the reasoning capabilities enabled by this geometry.

\bibliographystyle{plainnat}
\bibliography{references}

\end{document}
